Coherent optical creation of a single molecule

### 2020-12-04 paper.tex
Tweak up Raman Rabi vs Scattering plot and caption

\begin{figure*}
  \includegraphics[width=\textwidth]{imgs/fig-theory.pdf}
  \caption{Optical creation of single molecule from single atoms in tweezer.
    (a) Schematic of the optical transition from an atom pair to a weakly bound molecule.
    The initial state is the relative motional ground state between the two atoms
    and the final state is the first molecular bound state.
    The transition is driven by a pair of laser frequencies matching the binding energy
    of the molecule.
    The lasers are detuned from an excited molecular state in the $\mathrm{c^3\Sigma}$ potential
    by $\Delta$ in order to suppress scattering during the transfer.
    (b) Comparison between using a weakly bound and a deeply bound excited state
    as intermediate state for the Raman transition.
    The deeply bound excited state (blue lines $v'=0$)
    has a smaller Raman Rabi frequency ($\Omega_{R}$)
    compared to the weakly bound excited state (orange lines $v'=40$) at a most detuning.
    However, the scattering rate ($\Gamma_{s}$) is also much lower,
    which results in a larger ratio of Raman Rabi frequency to scattering rate.
    (c) Enhancement of the short-range wavefunction.
    The large scattering length for the $\Na(2,2),\Cs(3,3)$ state creates an interaction shift
    comparable to the axial trapping frequency.
    This causes a significant change in the relative wavefunction, especially at short
    internuclear distance ($R$).
    Compared to other spin states with weaker interaction,
    the wavefunction at short distance ($R<100\ \text{\AA}$, left of the dashed line)
    is significantly enhanced.
    \label{f-theory}
  }
\end{figure*}

>>>>

\begin{figure*}
  \includegraphics[width=\textwidth]{imgs/fig-theory.pdf}
  \caption{Optical creation of single molecule from single atoms in tweezer.
    (a) Schematic of the optical transition from an atom pair to a weakly bound molecule.
    The initial state is the relative motional ground state between the two atoms
    and the final state is the first molecular bound state.
    The transition is driven by a pair of laser frequencies matching the binding energy
    of the molecule.
    The lasers are detuned from an excited molecular state in the $\mathrm{c^3\Sigma}$ potential
    by $\Delta$ in order to suppress scattering during the transfer.
    (b) Comparison between using a weakly bound and a deeply bound excited state
    as intermediate state for the Raman transition.
    The deeply bound excited state (blue lines $v'=0$)
    has a larger ratio of Raman Rabi frequency to scattering rate
    compared to the weakly bound excited state (orange lines $v'=40$) at a most detuning.
    (c) Enhancement of the short-range wavefunction.
    The large scattering length for the $\Na(2,2),\Cs(3,3)$ state creates an interaction shift
    comparable to the axial trapping frequency.
    This causes a significant change in the relative wavefunction, especially at short
    internuclear distance ($R$).
    Compared to other spin states with weaker interaction,
    the wavefunction at short distance ($R<100\ \text{\AA}$, left of the dashed line)
    is significantly enhanced.
    \label{f-theory}
  }
\end{figure*}
